wind_diagrams

### 2019-11-30 wind_analyses.Rmd
update
updated commit

save(wind_months, file = "Data/wind_months.RData")
```

>>>>

# save(wind_months, file = "Data/wind_months.RData")
```

# Question:
  # Are there more SE winds in summer but comes later in January?I.e any changes in SE wind and changes in water temperature

```{r}
load("Data/SACTN_US.RData")
load("Data/wind_months.RData")

match_func <- function(df){
  match <- SACTN_US  %>%  
  left_join(df, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}

wind_months <- wind_months %>% 
  dplyr::rename(site = temp_sites)

wind_match <- match_func(df = wind_months) 
```
